---
title: "DECRAEMER"
author: "Julie decraemer"
format: html
---
```{r}
here::i_am("test-grades.Rproj")
library(here)
library(vroom)
library(ggplot2)
library(dplyr)
library(tidyr)
```
## Introduction
### Question 1
```{r}
grades <- vroom(here("grades.csv"))
```
## Simple analyses
### Question 2
```{r}
nrow(grades)
```
The data set contains 48090 grades.

### Question 3
```{r}
grades %>%
  distinct(id)
```
There are 749 students observed in this data set.

### Question 4
```{r}
students <- grades %>%
  select(id, group) %>%
  distinct()
```
Here is a sample of the students data frame:
```{r}
head(students)
```

### Question 5
```{r}
group_counts <- students %>%
  count(group)

ggplot(group_counts, aes(x = factor(group), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Group", y = "Number of Students", title = "Number of Students per Group") +
  theme_minimal()
```

### Question 6
```{r}
darknet_grades <- grades %>%
  filter(course == "Darknet Culture and Subversive Technologies")

average_grades <- darknet_grades %>%
  group_by(group) %>%
  summarise(average_grade = mean(grade, na.rm = TRUE))

ggplot(average_grades, aes(x = factor(group), y = average_grade)) +
  geom_col() +
  labs(x = "Group", y = "Average Grade", title = "Average Grade in DCST by Group") +
  theme_minimal()
```
### Question 7
```{r}
ggplot(grades, aes(x = grade, fill = factor(semester))) +
  geom_density(alpha = 0.5) +
  labs(x = "Grade", y = "Density", 
       title = "Distribution of Grades by Semester",
       fill = "Semester") +
  theme_minimal()
```
The grade distributions for the two semesters show notable differences. Semester 1 has a more concentrated distribution around scores between 10 and 12, while Semester 2 is more spread out and reaches higher scores near 20. This suggests that students may have achieved more varied and potentially higher results in Semester 2, indicating possible differences in course difficulty or evaluation standards across semesters.

## Attendance analysis
### Question 8
```{r}
grades_per_student <- grades %>%
  group_by(id, group) %>%
  summarise(num_grades = n(), .groups = "drop")

head(grades_per_student)
```
```{r}
student_grade_stats <- grades %>%
  group_by(id, group) %>%
  summarise(
    min_grade = min(grade),
    max_grade = max(grade),
    avg_grade = mean(grade),
    median_grade = median(grade),
    .groups = "drop"  # This drops the grouping after summarising
  )
knitr::kable(head(student_grade_stats, 10), caption = "Grade Statistics per Student (Sample)")
```
### Question 9
```{r}
philosophy_grades <- grades %>%
  filter(course == "Post-Human Philosophy and Ethics") %>%
  group_by(id, group) %>%
  summarise(
    num_grades = n(),
    .groups = "drop"
  )
knitr::kable(head(philosophy_grades, 10))
```
### Question 10
```{r}
grades_distribution <- philosophy_grades %>%
  count(num_grades, name = "num_students")

ggplot(grades_distribution, aes(x = num_grades, y = num_students)) +
  geom_col() +
  labs(
    x = "Number of Grades",
    y = "Number of Students",
    title = "Distribution of the Number of Grades in PHPE"
  ) +
  theme_minimal()
```
### Question 11
```{r}
ggplot(grades_per_student, aes(x = factor(group), y = num_grades)) +
  geom_boxplot(fill = "skyblue", color = "darkblue") +
  labs(
    x = "Group",
    y = "Number of Grades",
    title = "Distribution of Number of Grades per Student in PHPE by Group"
  ) +
  theme_minimal()
```
The median number of grades is fairly consistent across most groups, so students across different groups receive a similar number of grades in Post-Human Philosophy and Ethics. There is some variation in the spread of grades across groups. Finally, groups such as 1, 3, and 8 contains outliers that represent students who received fewer grades compared to their peers in the same group. This suggests that the number of grades per student in Post-Human Philosophy and Ethics does not depend on the group.

## Grade analysis
### Question 12
```{r}
average_grades <- grades %>%
  group_by(id, group, course) %>%
  summarise(avg_grade = mean(grade), .groups = "drop")

wide_grades <- average_grades %>%
  pivot_wider(names_from = course, values_from = avg_grade)

extract <- wide_grades %>%
  select(id, group, `Artificial Intelligence and Machine Learning`, `Bioengineering and Genetic Modification`)

print(extract)
```

### Question 13
```{r}
average_grades_plot <- wide_grades %>%
  select(id, group, `Artificial Intelligence and Machine Learning`, `Post-Human Philosophy and Ethics`)

ggplot(average_grades_plot, aes(x = `Post-Human Philosophy and Ethics`, y = `Artificial Intelligence and Machine Learning`)) +
  geom_point(color = "darkgrey", size = 2, alpha = 0.4) + 
  geom_smooth(method = "lm", formula = y ~ x, color = "steelblue", se = FALSE, linetype = "dashed") + 
  labs(
    x = "Average Grade in Post-Human Philosophy and Ethics",
    y = "Average Grade in AIML",
    title = "Comparison of Average Grades in Two Courses"
  ) +
  theme_minimal()
```
### Question 14
```{r}
colnames(average_grades)
```
```{r}
wide_grades <- average_grades %>%
  pivot_wider(names_from = course, values_from = avg_grade)

correlations <- wide_grades %>%
  group_by(group) %>%
  summarize(
    correlation = cor(`Artificial Intelligence and Machine Learning`, `Virtual Reality and Augmented Reality`, use = "complete.obs")
  )

print(correlations)
```

### Question 15
```{r}
target_group <- correlations %>%
  slice_max(abs(correlation), n = 1) %>%
  pull(group)

target_data <- wide_grades %>%
  filter(group == target_group)

ggplot(target_data, aes(x = `Virtual Reality and Augmented Reality`, y = `Artificial Intelligence and Machine Learning`)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "#E6E6FA") +
  labs(
    x = "Average Grades in Virtual Reality and Augmented Reality",
    y = "Average Grades in AI and ML",
    title = paste("Relationship Between AI & ML and VR & AR for Group", target_group)
  ) +
  theme_minimal()
```

### Question 16
```{r}
final_grades <- average_grades %>%
  group_by(id, group) %>%
  summarise(final_grade = mean(avg_grade), .groups = "drop") %>%
  arrange(desc(final_grade))
```
```{r}
head(final_grades, 5)
```
### Question 17
```{r}
ggplot(final_grades, aes(x = factor(group), y = final_grade)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  labs(x = "Group", y = "Final Grade", title = "Distribution of Final Grades by Group") +
  theme_minimal()
```
The distribution of final grades varies across groups, with some groups showing higher median grades and less variability, indicating potential differences in overall performance and consistency among groups.

