---
title: "DECRAEMER"
author: "Julie decraemer"
format: html
---
```{r}
here::i_am("test-grades.Rproj")
library(here)
library(vroom)
library(ggplot2)
library(dplyr)
library(tidyr)
```
## Introduction
### Question 1
```{r}
grades <- vroom(here("grades.csv"))
```
## Simple analyses
### Question 2
```{r}
nrow(grades)
```
The data set contains 48090 grades.

### Question 3
```{r}
grades %>%
  distinct(id)
```
There are 749 students observed in this data set.

### Question 4
```{r}
students <- grades %>%
  select(id, group) %>%
  distinct()
```
Here is a sample of the students data frame:
```{r}
head(students)
```

### Question 5
```{r}
group_counts <- students %>%
  count(group)

ggplot(group_counts, aes(x = factor(group), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Group", y = "Number of Students", title = "Number of Students per Group") +
  theme_minimal()
```

### Question 6
```{r}
darknet_grades <- grades %>%
  filter(course == "Darknet Culture and Subversive Technologies")

average_grades <- darknet_grades %>%
  group_by(group) %>%
  summarise(average_grade = mean(grade, na.rm = TRUE))

ggplot(average_grades, aes(x = factor(group), y = average_grade)) +
  geom_col() +
  labs(x = "Group", y = "Average Grade", title = "Average Grade in DCST by Group") +
  theme_minimal()
```
### Question 7
```{r}
ggplot(grades, aes(x = grade, fill = factor(semester))) +
  geom_density(alpha = 0.5) +
  labs(x = "Grade", y = "Density", 
       title = "Distribution of Grades by Semester",
       fill = "Semester") +
  theme_minimal()
```
The grade distributions for the two semesters show notable differences. Semester 1 has a more concentrated distribution around scores between 10 and 12, while Semester 2 is more spread out and reaches higher scores near 20. This suggests that students may have achieved more varied and potentially higher results in Semester 2, indicating possible differences in course difficulty or evaluation standards across semesters.

## Attendance analysis
### Question 8
```{r}
grades_per_student <- grades %>%
  group_by(id, group) %>%
  summarise(num_grades = n(), .groups = "drop")

head(grades_per_student)
```
```{r}
student_grade_stats <- grades %>%
  group_by(id, group) %>%
  summarise(
    min_grade = min(grade),
    max_grade = max(grade),
    avg_grade = mean(grade),
    median_grade = median(grade),
    .groups = "drop"  # This drops the grouping after summarising
  )
knitr::kable(head(student_grade_stats, 10), caption = "Grade Statistics per Student (Sample)")
```

